Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
Consistently capitalise Eden.

Cog's Mark-Compact algorithm, named \emph{SpurPlanningCompactor}, implements the classic planning compaction algorithm for Spur.  It uses the fact that there is room for a forwarding pointer in all objects to store the eventual position of an object in the first field. It therefore first locates a large free chunk, or eden or a memory segment, to use as the savedFirstFieldsSpace, which it uses to store the first fields of objects that will be compacted, these fields being overwritten by each object's eventual position. It then makes at least three passes through the heap.

@@

We evaluated the Moose benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by analysing the wildfly code base\footnote{http://www.wildfly.org/}. We distinguish four configurations:
\begin{itemize}
\item \emph{Sweep}: VM with standard GC parameters and the Mark-Sweep algorithm.
\item \emph{Compact}: VM with standard GC parameters and the Mark-Compact algorithm.
\item \emph{Compact-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Compact algorithm.
\item \emph{Sweep-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Sweep algorithm.
\end{itemize}
With a larger eden, more overall memory is used (in our case 90 extra Mb are used), but scavenge time is expected to be lower. Indeed, the scavenger is an implementation of Ungar's scavenger~\cite{Scavenger} and the scavenge time is proportional to the number of surviving objects.
%To evaluate the performance, we use:
%\begin{itemize}
%	\item the production VM generated by the CI of opensmalltalk-vm\footnote{https://github.com/OpenSmalltalk/opensmalltalk-vm}, that we call Mark-Compact or Compact.
%	\item a custom compiled VM, which features a different compactor, that we call Mark-Sweep or Sweep.
%\end{itemize}

>>>>

Cog's Mark-Compact algorithm, named \emph{SpurPlanningCompactor}, implements the classic planning compaction algorithm for Spur.  It uses the fact that there is room for a forwarding pointer in all objects to store the eventual position of an object in the first field. It therefore first locates a large free chunk, or Eden or a memory segment, to use as the savedFirstFieldsSpace, which it uses to store the first fields of objects that will be compacted, these fields being overwritten by each object's eventual position. It then makes at least three passes through the heap.

@@

We evaluated the Moose benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by analysing the wildfly code base\footnote{http://www.wildfly.org/}. We distinguish four configurations:
\begin{itemize}
\item \emph{Sweep}: VM with standard GC parameters and the Mark-Sweep algorithm.
\item \emph{Compact}: VM with standard GC parameters and the Mark-Compact algorithm.
\item \emph{Compact-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Compact algorithm.
\item \emph{Sweep-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Sweep algorithm.
\end{itemize}
With a larger Eden, more overall memory is used (in our case 90 extra Mb are used), but scavenge time is expected to be lower. Indeed, the scavenger is an implementation of Ungar's scavenger~\cite{Scavenger} and the scavenge time is proportional to the number of surviving objects.
%To evaluate the performance, we use:
%\begin{itemize}
%	\item the production VM generated by the CI of opensmalltalk-vm\footnote{https://github.com/OpenSmalltalk/opensmalltalk-vm}, that we call Mark-Compact or Compact.
%	\item a custom compiled VM, which features a different compactor, that we call Mark-Sweep or Sweep.
%\end{itemize}
